Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-10-29 paper.tex
Minor changes

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities ($S_{\nu}$
units) at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

>>>>

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.
